Designing and Developing a Personalised Recommender System

### 2021-02-09 paper/paper.tex
implemented SVD and can now see more info about restaurant

\subsection{Hybrid scheme}
Which two algorithms
A hybrid scheme is a good way to design a recommender system, since you can get the
best of both algorithms if done properly.
Meaning better recommendations than either algorithm could achieve individually.
Meta-level HRS with collaborative and content-based, or 
Cascade with knowledge-based and collaborative
Feature Augmentation with Knowledge Based and Collaborative

>>>>

\subsection{Hybrid scheme}
Which two algorithms
A hybrid scheme is a good way to design a recommender system, since you can get the
best of both algorithms if done properly. 
I am using a Cascade Hybrid Recommender System, since this has been shown to accurate predictions 
in my domain of restaurant recommendations \cite{burke2007hybrid}. 
The two systems are Collaborative Filtering and Content Based.

Meaning better recommendations than either algorithm could achieve individually.
Cascade with knowledge-based and collaborative
